\textbf{Automated Reasoning\\Practical Assignment -- Part 1}

### 2022-11-17 part2/report/paper.tex
Report and robot

>>>>

\section{Groups} % (fold)
\label{sec:groups}
\begin{enumerate}[label=\alph*)]
\item 
	Using prover9 we can prove that $I*x=x$, $inv(inv(x))=x$ and $inv(x)*x=I$.\\
	However, it is not true in general that $inv(x*y)=inv(x)*inv(y)$.\\
	The smallest group for which this does not hold has size $6$.
\item 
	The smallest non-Abelian group has size $6$.
\item 
	For $n=2$ all such groups are Abelian.\\
	For $n=3$ the group is not Abelian in general and the smallest counterexample has size $27$.\\
	For $n=4$ the group is not Abelian and the smallest counterexample has size $8$.
\end{enumerate}
% section groups (end)
